Interval Probability for Fuzzy Quantum Theories

### 2016-05-13 prob.tex
prob.tex \subsection{Quantum Probability Measures} updated...

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu_{\phi}$ as follows:
\[
\mu_{\phi}(E)=\ip{\phi}{E\phi}
\]
Moreover, the Born rule can be extended to a mixed state~$\rho$.
If the density matrix of a mixed state~$\rho$ can be expressed as
a convex combination of pure states, i.e., $\rho=\sum_{j=1}^{N}q_{j}\proj{\psi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$, then the probability measure induced
by $\rho$ can be expressed as a convex combination as well~\cite{peres1995quantum,544199}:
\begin{eqnarray}
\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

Conversely, Gleason's theorem states that given a probability measure
$\mu$, there exist a mixed state~$\rho$ that induces such a measure
using the Born rule. The theorem is only valid in Hilbert spaces with
dimension $d\geq3$. It is instructive to study counterexamples in
$d=2$, i.e., the case of a one-qubit system.

\begin{example}[One-qubit quantum probability measure] 
Consider a quantum probability
measure~$\mu:\events\rightarrow[0,1]$ defined as follow:
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as $\mu_{\ket{0}}$ which is a probability measure, we only
need to check $E=\proj{\ps}$ and $E=\proj{\ms}$. $\proj{\ps}$ and
$\proj{\ms}$ are only orthogonal to each other, and we have 
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1
\]
which satisfies the conditions as a probability measure. On the other
hand, $\mu$ cannot be induced by any mixed state because 
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
state and $\rho=E$.
\qed\end{example}

>>>>

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu_{\phi}$ as follows:
\[
\mu_{\phi}(E)=\ip{\phi}{E\phi}
\]

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$, then
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

Conversely, Gleason's theorem states that given a probability measure
$\mu$, there exist a mixed state~$\rho$ that induces such a measure
using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
The theorem is only valid in Hilbert spaces with dimension $d\geq3$.
It is instructive to study counterexamples in $d=2$, i.e., the case
of a one-qubit system.

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\mu_{\ket{0}}$, we only need
to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$: 
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
state and $\rho=E$. \qed\end{example}
